---
title: "Developing Data Products Course Project"
author: "Jack"
date: '`r Sys.Date()`'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is the final course project of the Developing Data Products course in the Coursera Data Science Specialisation.

It has been prepared using Slidify in RStudio.

The Shiny application is [here](https://osrjh.shinyapps.io/DevelopingDataProductsCourseProject/)

The Shiny app code is [here](https://github.com/osrjh/Developing-Data-Prodcts-Course-Project)

* The app was created using Shiny.

* The source code is split up into two files 
  + server.R (back-end)
  + ui.R (user-interface)

## App Functions

* Allows you to plot numeric factors against fuel consumption using the mtcars dataset.

```{r, echo = T}
head(mtcars)
```

* You select variables for plotting and building simple linear models. 

* The output is a scatterplot with a prediction of miles per gallon calculated using the regression models. 

## App Layout

* There are two panels on the app
  + Side panel (on the left)
  + Main panel
  
* The main panel has a brief summary and instructions on how to use the app. It also features the scatterplot and predicted value.

---

* The side panel lists the available variables in the dataset, features dropdowns to select the dependent variable and scatterplot fill option. 

* There are also checkboxes to show/hide the plot labels.

* The slider will change depending on the variable selected and can be used to alter the value of the dependent variable when inserted into the regression formula.

* Finally, the slope and the intercept of the regression formula are listed at the bottom.

